---
title: "R Notebook"
output: html_notebook
---


```{r}
rm(list=ls())
devtools::load_all()
```

Annual model

```{r}

######################
# generate monthly rainfall 

clim = convert_climYMD_POSIXct(tank_obs)

P.zoo = zoo::zoo(clim$P,clim$times)
P.zoo.mon = aggregate(P.zoo,zoo::as.yearmon,sum)
times.mon = time(P.zoo.mon)
clim_mon = list(times=as.POSIXct(times.mon,tz = 'UTC'),
                P=zoo::coredata(P.zoo.mon))

####################
# setup seasonal monAR1 model

modelSelection = list()
modelSelection$modelType = list()
modelSelection$modelType$P = "monAR1"
modelSelection$modelParameterVariation = list()
modelSelection$modelParameterVariation$P = "ann"

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

####################

attPerturb = c("P_month_all_tot_m")
attHold = c("P_month_all_P50","P_month_all_P90","P_month_all_cor")

attPerturbType = "regGrid"
attPerturbSamp = c(1)
attPerturbMin = c(1)
attPerturbMax = c(1)

# create the exposure space
expSpace = createExpSpace(attPerturb = attPerturb,
                          attPerturbSamp = attPerturbSamp,
                          attPerturbMin = attPerturbMin,
                          attPerturbMax = attPerturbMax,
                          attPerturbType = attPerturbType,
                          attHold = attHold)

####################

sim_stoch = generateScenarios(reference = clim_mon,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)

plotScenarios(sim_stoch)



```
Annual model - synthetic 

```{r}

par = sim_stoch$Rep1$Target1$P$par
#par = c(400,200,0.2,1)

# modelSelection[["modelParameterBounds"]] <- list()
# modelSelection[["modelParameterBounds"]][["P"]] <- list()
# modelSelection[["modelParameterBounds"]][["P"]][["mu.SON"]] = c(400,400)
# modelSelection[["modelParameterBounds"]][["P"]][["mu.DJF"]] = c(400,400)
# modelSelection[["modelParameterBounds"]][["P"]][["mu.MAM"]] = c(400,400)
# modelSelection[["modelParameterBounds"]][["P"]][["mu.JJA"]] = c(400,400)
# modelSelection[["modelParameterBounds"]][["P"]][["sigma.SON"]] = c(200,200)
# modelSelection[["modelParameterBounds"]][["P"]][["sigma.DJF"]] = c(200,200)
# modelSelection[["modelParameterBounds"]][["P"]][["sigma.MAM"]] = c(200,200)
# modelSelection[["modelParameterBounds"]][["P"]][["sigma.JJA"]] = c(200,200)
# modelSelection[["modelParameterBounds"]][["P"]][["phi.SON"]] = c(0.2,0.2)
# modelSelection[["modelParameterBounds"]][["P"]][["phi.DJF"]] = c(0.2,0.2)
# modelSelection[["modelParameterBounds"]][["P"]][["phi.MAM"]] = c(0.2,0.2)
# modelSelection[["modelParameterBounds"]][["P"]][["phi.JJA"]] = c(0.2,0.2)
# modelSelection[["modelParameterBounds"]][["P"]][["lambda.SON"]] = c(1,1)
# modelSelection[["modelParameterBounds"]][["P"]][["lambda.DJF"]] = c(1,1)
# modelSelection[["modelParameterBounds"]][["P"]][["lambda.MAM"]] = c(1,1)
# modelSelection[["modelParameterBounds"]][["P"]][["lambda.JJA"]] = c(1,1)

# modelSelection[["modelParameterBounds"]] <- list()
# modelSelection[["modelParameterBounds"]][["P"]][["mu"]] = c(300,500)
# modelSelection[["modelParameterBounds"]][["P"]][["sigma"]] = c(100,300)
# modelSelection[["modelParameterBounds"]][["P"]][["phi"]] = c(0.1,0.3)
# modelSelection[["modelParameterBounds"]][["P"]][["lambda"]] = c(0.5,1.5)

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

datInd = list(month=get.date.ind(times=clim_mon$times))

set.seed(1)
P=simClim(parS=par,modelTag='P-ann-monAR1',datInd =datInd,randomTerm=list(randomVector=runif(length(clim_mon$times))))

climSynth = list(times=clim_mon$times,P=P)

sim_synth = generateScenarios(reference = climSynth,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)

plotScenarios(sim_synth)

```



Seasonal model

```{r}

######################
# generate monthly rainfall 

clim = convert_climYMD_POSIXct(tank_obs)

P.zoo = zoo::zoo(clim$P,clim$times)
P.zoo.mon = aggregate(P.zoo,zoo::as.yearmon,sum)
times.mon = time(P.zoo.mon)
clim_mon = list(times=as.POSIXct(times.mon,tz = 'UTC'),
                P=zoo::coredata(P.zoo.mon))

####################
# setup seasonal monAR1 model

modelSelection = list()
modelSelection$modelType = list()
modelSelection$modelType$P = "monAR1"
modelSelection$modelParameterVariation = list()
modelSelection$modelParameterVariation$P = "seas"

# # specify the penalty settings in a list
# modelSelection[["penaltyAttributes"]] <- c("P_month_all_tot_m","P_month_all_P50","P_month_all_P90","P_month_all_cor")
# modelSelection[["penaltyWeights"]] <- c(2,2,2,2)

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

####################

# attPerturb = c("P_month_all_tot_m")
# attHold = c("P_month_all_P50","P_month_all_P90","P_month_all_cor",
#            "P_month_DJF_tot_m","P_month_DJF_P50","P_month_DJF_P90","P_month_DJF_cor",
#            "P_month_MAM_tot_m","P_month_MAM_P50","P_month_MAM_P90","P_month_MAM_cor",
#            "P_month_JJA_tot_m","P_month_JJA_P50","P_month_JJA_P90","P_month_JJA_cor",
#            "P_month_SON_tot_m","P_month_SON_P50","P_month_SON_P90","P_month_SON_cor")

attPerturb = c("P_month_DJF_tot_m")
attHold = c("P_month_DJF_P50","P_month_DJF_P90","P_month_DJF_cor",
           "P_month_MAM_tot_m","P_month_MAM_P50","P_month_MAM_P90","P_month_MAM_cor",
           "P_month_JJA_tot_m","P_month_JJA_P50","P_month_JJA_P90","P_month_JJA_cor",
           "P_month_SON_tot_m","P_month_SON_P50","P_month_SON_P90","P_month_SON_cor")

attPerturbSamp = c(1)
attPerturbMin = c(1)
attPerturbMax = c(1)

# create the exposure space
expSpace = createExpSpace(attPerturb = attPerturb,
                          attPerturbSamp = attPerturbSamp,
                          attPerturbMin = attPerturbMin,
                          attPerturbMax = attPerturbMax,
                          attPerturbType = attPerturbType,
                          attHold = attHold)

####################

sim_stoch_seas = generateScenarios(reference = clim_mon,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)

plotScenarios(sim_stoch_seas)

clim_sim_stoch_seas = list(times=clim_mon$times,P=sim_stoch_seas$Rep1$Target1$P$sim)

attSel = c("P_month_all_tot_m","P_month_all_P50","P_month_all_P90","P_month_all_cor")

calculateAttributes(clim_mon,attSel)
calculateAttributes(clim_sim_stoch_seas,attSel)

```
adding annual attributes to calibration

add initial parameter values based on cal without annual atts

```{r}

modelSelection[["optimisationArguments"]] = list()
modelSelection[["optimisationArguments"]]$suggestions = sim_stoch_seas$Rep1$Target1$P$par

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

attPerturb = c("P_month_all_tot_m")
attHold = c("P_month_all_P50","P_month_all_P90","P_month_all_cor",
           "P_month_DJF_tot_m","P_month_DJF_P50","P_month_DJF_P90","P_month_DJF_cor",
           "P_month_MAM_tot_m","P_month_MAM_P50","P_month_MAM_P90","P_month_MAM_cor",
           "P_month_JJA_tot_m","P_month_JJA_P50","P_month_JJA_P90","P_month_JJA_cor",
           "P_month_SON_tot_m","P_month_SON_P50","P_month_SON_P90","P_month_SON_cor")

attPerturbSamp = c(1)
attPerturbMin = c(1)
attPerturbMax = c(1)

# create the exposure space
expSpace = createExpSpace(attPerturb = attPerturb,
                          attPerturbSamp = attPerturbSamp,
                          attPerturbMin = attPerturbMin,
                          attPerturbMax = attPerturbMax,
                          attPerturbType = attPerturbType,
                          attHold = attHold)

####################

sim_stoch_seas.1 = generateScenarios(reference = clim_mon,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)

plotScenarios(sim_stoch_seas.1)

```
can't get both seasonal and annual attributes right with this model

______________


Seasonal model with annual phi

```{r}

######################
# generate monthly rainfall 

clim = convert_climYMD_POSIXct(tank_obs)

P.zoo = zoo::zoo(clim$P,clim$times)
P.zoo.mon = aggregate(P.zoo,zoo::as.yearmon,sum)
times.mon = time(P.zoo.mon)
clim_mon = list(times=as.POSIXct(times.mon,tz = 'UTC'),
                P=zoo::coredata(P.zoo.mon))

####################
# setup seasonal monAR1 model

modelSelection = list()
modelSelection$modelType = list()
modelSelection$modelType$P = "monAR1"
modelSelection$modelParameterVariation = list()
modelSelection$modelParameterVariation$P = "seas1"

# specify the penalty settings in a list
modelSelection[["penaltyAttributes"]] <- c("P_month_all_tot_m","P_month_all_P50","P_month_all_P90","P_month_all_cor")
modelSelection[["penaltyWeights"]] <- c(2,2,2,2)

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

####################

attPerturb = c("P_month_all_tot_m")
attHold = c("P_month_all_P50","P_month_all_P90","P_month_all_cor",
           "P_month_DJF_tot_m","P_month_DJF_P50","P_month_DJF_P90",
           "P_month_MAM_tot_m","P_month_MAM_P50","P_month_MAM_P90",
           "P_month_JJA_tot_m","P_month_JJA_P50","P_month_JJA_P90",
           "P_month_SON_tot_m","P_month_SON_P50","P_month_SON_P90")

attPerturbSamp = c(1)
attPerturbMin = c(1)
attPerturbMax = c(1)

# create the exposure space
expSpace = createExpSpace(attPerturb = attPerturb,
                          attPerturbSamp = attPerturbSamp,
                          attPerturbMin = attPerturbMin,
                          attPerturbMax = attPerturbMax,
                          attPerturbType = attPerturbType,
                          attHold = attHold)

####################

sim_stoch_seas1 = generateScenarios(reference = clim_mon,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)#,simLengthNyrs = 1000)

plotScenarios(sim_stoch_seas1)

clim_sim_stoch_seas1 = list(times=clim_mon$times,P=sim_stoch_seas1$Rep1$Target1$P$sim)

# attSel = c("P_month_all_tot_m","P_month_all_P50","P_month_all_P90","P_month_all_cor")
# 
# calculateAttributes(clim_mon,attSel)
# calculateAttributes(clim_sim_stoch_seas,attSel)

```
Above results show that we can't get both seasonal attributes and annual attributes right.


_______________________________________________

Seasonal model - synthetic 

```{r}

par = sim_stoch_seas1$Rep1$Target1$P$par

datInd = list(month=get.date.ind(times=clim_mon$times))

set.seed(1)
P=simClim(parS=par,modelTag='P-seas1-monAR1',datInd =datInd,randomTerm=list(randomVector=runif(length(clim_mon$times))))

climSynth = list(times=clim_mon$times,P=P)

modelSelection[["optimisationArguments"]] = list()
modelSelection[["optimisationArguments"]]$suggestions = par

modelSelectionJSON = jsonlite::toJSON(modelSelection, pretty = TRUE, auto_unbox = TRUE)
controlFile = paste0(tempdir(), "\\eg_controlFile.json")
write(modelSelectionJSON, file = controlFile)

sim_synth_seas1 = generateScenarios(reference = climSynth,
                             expSpace = expSpace,
                             controlFile = controlFile,
                             seedID=1)

plotScenarios(sim_synth_seas1)

```